---
title: "Covid-19 prediction"
author: "Kirill Setdekov"
date: "12 04 2020"
output:
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages
```{r libload, message=FALSE, warning=FALSE}
library(caret)
library(dplyr)
library(readr)
library(party)
require(randomForest)
```

Load data
```{r loaddata}
enriched <-
        read_csv("input/covid19-enriched-dataset-week-2/enriched_covid_19_week_2.csv")
head(enriched[, 1:10])
test <-
        read_csv("input/covid19-global-forecasting-week-4/test.csv",
                 col_types = cols(Date = col_date(format = "%Y-%m-%d")))
submission <-
        read_csv("input/covid19-global-forecasting-week-4/submission.csv")
train <-
        read_csv("input/covid19-global-forecasting-week-4/train.csv")
head(test)
head(train)
```
take a look at Russia
```{r}
enriched %>% filter(Country_Region == "Russia") %>% head()
enriched_countries <- enriched$Country_Region %>% unique()
train_countries <- train$Country_Region %>% unique() 
train_countries_df <- data.frame(train_countries)
train_countries_df <- train_countries_df %>% mutate(isinenriched = ifelse(train_countries %in% enriched_countries,1,0))
```
Data is constant over time. We can leftjoin in to the train data and replicate the last row

Need data transformation:
4 countries are more detailed in enriched data
* Australia - all values aggreaged over regions, starting with Australia
* Canada - all values aggreaged over regions, starting with Canada
* China - all values aggreaged over regions, starting with China
* US - all values aggreaged over regions, starting with US

```{r aggregation, message=FALSE, warning=FALSE}
australia_names <- enriched_countries[9:16]
enriched$Country_Region[enriched$Country_Region %in% australia_names] <- "Australia"

canada_names <- enriched_countries[37:46]
enriched$Country_Region[enriched$Country_Region %in% canada_names] <- "Canada"


china_names <- enriched_countries[50:82]
enriched$Country_Region[enriched$Country_Region %in% china_names] <- "China"


us_names <- enriched_countries[225:278]
enriched$Country_Region[enriched$Country_Region %in% us_names] <- "US"


uk_names <- enriched_countries[282:287]
enriched$Country_Region[enriched$Country_Region %in% uk_names] <- "United Kingdom"

enriched$Country_Region[enriched$Country_Region %in% enriched_countries[109:117]] <- "France"

enriched$Country_Region[enriched$Country_Region %in% enriched_countries[92:93]] <- "Denmark"
enriched$Country_Region[enriched$Country_Region %in% enriched_countries[174:176]] <- "Netherlands"


# what dates we have?
enriched %>% group_by(Country_Region, Province_State) %>% select(Date) %>% summarise(max = max(Date), min = min(Date))
train %>% group_by(Country_Region, Province_State) %>% select(Date) %>% summarise(max = max(Date), min = min(Date))
test %>% group_by(Country_Region, Province_State) %>% select(Date) %>% summarise(max = max(Date), min = min(Date))

enriched <- enriched %>% select(-c("Id", "ConfirmedCases", "Fatalities"))
enriched_last_date <- enriched %>% filter(Date =="2020-03-25")
enriched_last_date <- enriched_last_date %>% select(-c("Date"))

rm(train_countries, train_countries_df, australia_names, canada_names, china_names, enriched_countries, train_countries, uk_names, us_names)
```

# join enriched data to train and test
```{r}
enrich <- function(df, enriched, enriched_last_date) {
        require(dplyr)
  p1 <- left_join(df, enriched, by = c("Province_State", "Country_Region", "Date"))
  p2 <- left_join(df, enriched_last_date, by = c("Province_State", "Country_Region"))
  p1 <- p1 %>% filter(Date <= "2020-03-25")
  p2 <- p2 %>% filter(Date > "2020-03-25")
  df <- bind_rows(p1,p2)
  rm(p1,p2)
  return(df)
}
train <- enrich(train, enriched, enriched_last_date)
test <- enrich(test, enriched, enriched_last_date)


```


11 are missing, will impute with knnImpute

* Botswana
* Burma
* Burundi
* Kosovo
* MS Zaandam	
* Malawi
* Sao Tome and Principe
* Sierra Leone
* South Sudan
* West Bank and Gaza
* Western Sahara

```{r}
# Use the imputation model to predict the values of missing data points
train_toedit <- as.data.frame(train[,7:38])
d <- preProcess(train_toedit, "medianImpute")
x1 <- predict(d, train_toedit)
train[,7:38] <- x1

test_toedit <- as.data.frame(test[,5:36])
x2 <- predict(d, test_toedit)
test[,5:36] <- x2
rm(x1, x2, test_toedit, train_toedit, d)


#generate date of first case
first_date <- train %>% group_by(Country_Region, Province_State) %>% select(ConfirmedCases, Fatalities, Date) %>% filter(ConfirmedCases >0) %>% summarise(date_1 = min(Date))
train <- left_join(train,first_date) %>% mutate(days_epi = ifelse(Date-date_1 >0, Date-date_1 ,0)) %>% select(-date_1)
test <- left_join(test,first_date) %>% mutate(days_epi = ifelse(Date-date_1 >0, Date-date_1 ,0)) %>% select(-date_1)


train <- train %>% mutate(region = as.factor(paste0(Country_Region,Province_State)), ConfirmedCases = log(ConfirmedCases+1), Fatalities = log(Fatalities + 1))
test <- test %>% mutate(region = as.factor(paste0(Country_Region,Province_State)))

train_stub <- train[,5:40]
test_stub <- test[,5:38]
```

#modelling
```{r}

mod1 <- train(ConfirmedCases~., method ="glm", data = train_stub[,c(1,3:36)])
mod2 <- train(ConfirmedCases~., method ="rf", data = train_stub[,c(1,3:36)], trControl = trainControl(method = "cv"),number = 3)
mod3 <- train(ConfirmedCases~., method ="rpart", data = train_stub[,c(1,3:36)])
mod4 <- train(ConfirmedCases~., method ="ctree", data = train_stub[,c(1,3:36)])
# mod5 <- mob(ConfirmedCases |.,data = as.data.frame(train_stub[,c(1,3:36)]))
mod6 <- train(ConfirmedCases~., method = "lm", data = train_stub[,c(1,3:36)])

pred1 <- predict(mod6, train_stub[train_stub$region=="RussiaNA",c(1,3:36)])
qplot(ConfirmedCases,pred1, data = train_stub[train_stub$region=="RussiaNA",])
```

